\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-23 pldi/draft.tex
Update plots
Update fig

\begin{figure}[t]
\centering
\includegraphics[width=0.49\textwidth]{\detokenize{./figs/dish_schematic.pdf}}
\caption{
  \textbf{\sys transformation overview.}
  Given a shell pipeline, \sys leverages command parallelizability to identify
  high-parallelizability stages, rewrite them, and orchestrate their execution.
  \todo{reference in txt/decide}.
}
\vspace{-15pt}
\label{fig:overview}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{\detokenize{./figs/dish_cat.pdf}}
\vspace{-28pt}
\caption{
  \textbf{Stateless parallelization transformation.}
  The \texttt{cat} node is commuted with the stateless node to utilize available data parallelism.
  \nv{Should graph be \emph{directed}?}
}
\vspace{-15pt}
\label{fig:parallelization-transformation}
\end{figure}

@@

\section{Annotation Language Grammar}
\label{alg}

\Cref{fig:dsl} shows the complete grammar of the parallelizability
annotation language.

\begin{figure}
  \centering
  \begin{grammar}
    <option> ::= `-' <string>

    <category> ::= `stateless' | `pure' | ...

    <maybe-int> ::= | <int>

    <arg> ::= `args[' <int> `]'

    <args> ::= <arg>
    \alt `args[' <maybe-int> `:' <maybe-int> `]'

    <input> ::= `stdin' | <args>

    <inputs> ::= <input>
    \alt <input> `,' <inputs>

    <output> ::= `stdout' | <arg>

    <outputs> ::= <output>
    \alt <output> `,' <outputs>

    <option-pred> ::= <option>
    \alt `value' <option> = <string>
    \alt `not' <option-pred>
    \alt <option-pred> `or' <option-pred>
    \alt <option-pred> `and' <option-pred>

    <assignment> ::= `(' <category>, `[' <inputs> `]' `,' `[' <output> `]' `)'

    <predicate> ::= <option-pred> `=>' <assignment>

    <pred-list> ::= `|' <predicate> <pred-list>
    \alt `|' `otherwise' `=>' <assignment>

    <command> ::= <name> `\{' <pred-list> `\}'

    <command-list> ::= <command>
    \alt <command> <command-list>
  \end{grammar}
  \caption{
  \textbf{Parallelizability description language.}
    The DSL captures important information regarding the parallelizability of a command.
  }
  \label{fig:dsl}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.49\textwidth]{\detokenize{./figs/dish_overview.pdf}}
\caption{
  \textbf{\sys overview.}
  A high-level schematic outline of \sys, and how this maps on the structure of this paper.
}
\vspace{-15pt}
\label{fig:overview}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{\detokenize{./figs/dish_cat.pdf}}
\vspace{-28pt}
\caption{
  \textbf{Stateless parallelization transformation.}
  The \texttt{cat} node is commuted with the stateless node to utilize available data parallelism.
}
\vspace{-15pt}
\label{fig:parallelization-transformation}
\end{figure}

@@

% \section{Annotation Language Grammar}
% \label{alg}
% 
% \Cref{fig:dsl} shows the complete grammar of the parallelizability
% annotation language.
% 
% \begin{figure}
%   \centering
%   \begin{grammar}
%     <option> ::= `-' <string>
% 
%     <category> ::= `stateless' | `pure' | ...
% 
%     <maybe-int> ::= | <int>
% 
%     <arg> ::= `args[' <int> `]'
% 
%     <args> ::= <arg>
%     \alt `args[' <maybe-int> `:' <maybe-int> `]'
% 
%     <input> ::= `stdin' | <args>
% 
%     <inputs> ::= <input>
%     \alt <input> `,' <inputs>
% 
%     <output> ::= `stdout' | <arg>
% 
%     <outputs> ::= <output>
%     \alt <output> `,' <outputs>
% 
%     <option-pred> ::= <option>
%     \alt `value' <option> = <string>
%     \alt `not' <option-pred>
%     \alt <option-pred> `or' <option-pred>
%     \alt <option-pred> `and' <option-pred>
% 
%     <assignment> ::= `(' <category>, `[' <inputs> `]' `,' `[' <output> `]' `)'
% 
%     <predicate> ::= <option-pred> `=>' <assignment>
% 
%     <pred-list> ::= `|' <predicate> <pred-list>
%     \alt `|' `otherwise' `=>' <assignment>
% 
%     <command> ::= <name> `\{' <pred-list> `\}'
% 
%     <command-list> ::= <command>
%     \alt <command> <command-list>
%   \end{grammar}
%   \caption{
%   \textbf{Parallelizability description language.}
%     The DSL captures important information regarding the parallelizability of a command.
%   }
%   \label{fig:dsl}
% \end{figure}
